---
title: "Coral survivorship under nutrients and heat stress"
author: "Ana Palacio"
date: "Nov 18, 2018"
output:
   html_document:
    df_print: paged
    fig_height: 7
    fig_width: 8
    toc: yes
nocite: '@*'
editor_options:
  chunk_output_type: console
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# General project set-up 

```{r libraries, results="hide"}

# Load all libraries and sources required to run the script
    library(tidyverse)
    library(ggthemes)
    library(survival)
    library(survminer)

# Default ggplot settings

    Fill.colour<-c("black", "#1A85FF", "#D41159")

    ggthe_bw<-theme(plot.background=element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          legend.box.background = element_rect(),
          panel.background =element_rect(fill = NA, color = "black")
          )+
    theme_bw()
  
```

# Acropora cervicornis

## Import data

```{r}
# Acer data
    Survival.data<-read.csv("Data/Acer_Mortality.csv", header = TRUE)
    summary(Survival.data)
    summary(Survival.data$Genotype)
    Survival.data$Genotype<-factor(Survival.data$Genotype, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    summary(Survival.data$Genotype)
```

## Create survival object

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object <- Surv(time = Survival.data$Fu.time_texp, event = Survival.data$Fu.stat_exp)
  surv_object 

```

## Nutrient treatment effect (A, N, N+P)

### Figure 2 (1st panel)

```{r}

# Only treatment model
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit1 <- survfit(surv_object ~ Treatment, data = Survival.data)
    summary(fit1)

    
    #coxfitAc <- coxph(surv_object ~ Treatment, data = Survival.data)
    #summary(coxfitAc)

    # Plot the survival model
    Ac_Treatment_Only<-ggsurvplot(fit1, data = Survival.data, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour,
           break.time.by=15, xlim=c(0,115), risk.table.y.text = FALSE,
           risk.table.title="Number of fragments at risk") + ggtitle("A. cervicornis")
    Ac_Treatment_Only
    
  Acer.Probabilities<-Ac_Treatment_Only$data.survplot

```

## Nutrient treatment effect (Compare N vs N+P)

```{r}
# Data
    Survival.data2<-Survival.data[(Survival.data$Treatment!="Ambient"),]
    summary(Survival.data2)
    summary(Survival.data2$Genotype)
    Survival.data2$Genotype<-factor(Survival.data2$Genotype, 
                                   levels=c("G_48", "G_62","G_31", "G_08","G_07", "G_50"))
    summary(Survival.data2$Genotype)
    summary(Survival.data2$Treatment)
    Survival.data2$Treatment<-factor(Survival.data2$Treatment, 
                                   levels=c("N", "N_P"))
```

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object2 <- Surv(time = Survival.data2$Fu.time_texp, 
                       event = Survival.data2$Fu.stat_exp)
  surv_object2 

```

```{r}
# Only treatment model
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit1_2 <- survfit(surv_object2 ~ Treatment, data = Survival.data2)
    summary(fit1_2)
    surv_pvalue(fit1_2)
    
    # Plot the survival model
    N_NP_Only<-ggsurvplot(fit1_2, data = Survival.data2, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour)
    N_NP_Only

```

```{r}
# Hazard ratio
  fit.coxph1_2 <- coxph(surv_object2 ~ Treatment, data = Survival.data2)
  ggforest(fit.coxph1_2, data = Survival.data2)
  fit.coxph1_2
```


# Orbicella faveolata 

## Import data

```{r}
# Data
    Survival.Of.data<-read.csv("Data/Ofav_Mortality.csv", header = TRUE)

    summary(Survival.Of.data)
    Survival.Of.data$Genotype<-factor(Survival.Of.data$Colony, 
                                      levels = c("Of_34", "Of_20", "Of_6", "Of_31"))
    summary(Survival.Of.data$Genotype)
```

## Create survival object

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object_Of <- Surv(time = Survival.Of.data$Fu.time_texp, 
                         event = Survival.Of.data$Fu.stat_exp)
  surv_object_Of 
```

## Nutrient treatment effect (A, N, N+P)

### Figure 2 (2nd panel)

```{r}
# Only treatment model
   # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit2_Of <- survfit(surv_object_Of ~ Treatment, data = Survival.Of.data)
    summary(fit2_Of)
    
   # Plot the survival model
    Of_Treatment_Only<-ggsurvplot(fit2_Of, data = Survival.Of.data, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour,
           break.time.by=15, xlim=c(0,115), risk.table.y.text = FALSE,
           risk.table.title="Number of fragments at risk") + ggtitle("O. faveolata") 
    Of_Treatment_Only
    
    #ggsave("Outputs/Ofav_Surv_Treatment_Of.svg", 
     #     Of_Treatment_Only$plot, width=4, height=3.5,dpi = 300)
    #ggsave("Outputs/Fig_SX4_Surv_Treatment_Of.pdf", print(Treatment_Only),
           #width=5, height=6,dpi = 300)
```

```{r}
# Hazard ratio
  fit.coxph1_3 <- coxph(surv_object_Of ~ Treatment, data = Survival.Of.data)
  ggforest(fit.coxph1_3, data = Survival.Of.data)
  fit.coxph1_3
  summary(fit.coxph1_3)
```

### Colony effect (Figure S4)

```{r}
# Only genotype model
  # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit3_Of <- survfit(surv_object_Of ~ Genotype, conf.type = "log-log", 
                    data = Survival.Of.data)
    summary(fit3_Of)
  # Plot the survival model
    Genotype_only_OF<-ggsurvplot(fit3_Of, data = Survival.Of.data, pval = TRUE,
               risk.table=T, tables.height=0.4, conf.int = T, n.risk   = TRUE )
    Genotype_only_OF
    
    Ofav.Probabilities<-Genotype_only_OF$data.survplot

# Treatment and genotype model 1 
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit4_Of <- survfit(surv_object_Of ~ Genotype + Treatment, data = Survival.Of.data)
    summary(fit4_Of)

    ggsurvplot_facet(fit4_Of, data = Survival.Of.data, facet.by="Genotype",
                     #risk.table=T, tables.height=0.5,
                 nrow = 4, alpha=1,
                 palette=Fill.colour, linetype=1)


    Ofav_PLot<- ggsurvplot_facet(fit4_Of, data = Survival.Of.data, 
                 facet.by="Treatment", 
                 # risk.table=T, tables.height=0.5, 
                 nrow = 3, alpha=0.5, conf.int = T,
                 linetype=1)+theme(legend.position = "left")
    Ofav_PLot
    
```


# Siderastrea siderea 

## Import data

```{r}
# Data
    Survival.Ss.data<-read.csv("Data/Ssid_Mortality.csv", header = TRUE)
    summary(Survival.Ss.data)
    Survival.Ss.data$Genotype<-factor(Survival.Ss.data$Colony, levels = c(
      "Ss_22", "Ss_23", "Ss_27", "Ss_28", "Ss_24", "Ss_30", "Ss_20"))
    summary(Survival.Ss.data$Genotype)
```

## Create survival object

```{r}
## Add survival object (Fit survival data using the Kaplan-Meier method)
  surv_object_SS <- Surv(time = Survival.Ss.data$Fu.time_texp, 
                         event = Survival.Ss.data$Fu.stat_exp)
  surv_object_SS 

```

## Nutrient treatment effect (A, N, N+P)

### Figure 2 (3rd panel)

```{r}
# Only treatment model
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit5Ss <- survfit(surv_object_SS ~ Treatment, data = Survival.Ss.data)
    summary(fit5Ss)
    
    coxfitSs <- coxph(surv_object_SS ~ Treatment, data = Survival.Ss.data)
    summary(coxfitSs)

    # Plot the survival model
    Ss_Treatment_Only<-ggsurvplot(fit5Ss, data = Survival.Ss.data, pval = TRUE, 
           conf.int = T, risk.table=T, palette=Fill.colour,
           break.time.by=15, xlim=c(0,115), risk.table.y.text = FALSE,
           risk.table.title="Number of fragments at risk") + ggtitle("S. siderea") 
    Ss_Treatment_Only
    #ggsave("Outputs/Fig_Ssid_Surv_Treatment.svg", 
           #Ss_Treatment_Only$plot, width=4, height=3.5,dpi = 300)

```

### Colony effect

```{r}

# Only genotype model
  # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit6Ss <- survfit(surv_object_SS ~ Genotype, conf.type = "log-log",
                      data = Survival.Ss.data)
    summary(fit6Ss)
  # Plot the survival model
    Genotype_only_SS<-ggsurvplot(fit6Ss, data = Survival.Ss.data, pval = TRUE,
               risk.table=T, tables.height=0.4, conf.int = T, n.risk   = TRUE )
    Genotype_only_SS

        
# Treatment and genotype model 1 
    # Kaplan-Meier estimator. The "log-log" confidence interval is preferred.
    fit7Ss <- survfit(surv_object_SS ~ Genotype + Treatment, data = Survival.Ss.data)
    summary(fit7Ss)
    # Plot the survival model
    Ssid_PLot<-ggsurvplot_facet(fit7Ss, data = Survival.Ss.data, 
                 facet.by="Treatment", 
                 # risk.table=T, tables.height=0.5, 
                 nrow = 3, alpha=0.5, conf.int = T,
                 linetype=1) +theme(legend.position = "left")
    Ssid_PLot
```

# Figure 2: All Spp treatment plot

```{r}
Survival.Trat.plot<-ggarrange(Ac_Treatment_Only$plot,
                              Of_Treatment_Only$plot, 
                              Ss_Treatment_Only$plot, 
                              Ac_Treatment_Only$table, 
                              Of_Treatment_Only$table, 
                              Ss_Treatment_Only$table,
                              heights = c(2, 0.7),
                              ncol = 3, nrow = 2)
Survival.Trat.plot

ggsave(file="Outputs/Survival.Treat.plot.svg", plot=Survival.Trat.plot, width=7.5, height=6)
```


# Supplementary plots by colonies (Symbiont communities)

```{r}
SuplementatySurvivalA<-ggarrange(Genotype_only_OF$plot,Genotype_only_SS$plot,
                                 Genotype_only_OF$table ,Genotype_only_SS$table,
                                 labels = c("O. faveolata", "S.siderea"),
                                 ncol = 2, nrow = 2)
SuplementatySurvivalA

SuplementatySurvivalB<-ggarrange(Ofav_PLot, Ssid_PLot, labels = c("O. faveolata", "S.siderea"),
          ncol = 2, nrow = 1)
SuplementatySurvivalB

```

# Packages used

```{r}
# Creates bibliography 
#knitr::write_bib(c(.packages()), "packages.bib")
```
